---
title: "Data Manipulation Part 1 - Exercises"
execute:
  echo: true
  messages: false
  warning: false
  cache: true
---

```{r}
#| label: load-packages
library(arrow)
library(dplyr)
library(stringr)
```

```{r}
#| label: open-dataset
nyc_taxi <- open_dataset("data/nyc-taxi")
nyc_taxi
```


# Using `collect()` to run a query

## Problems

Use the function `nrow()` to work out the answers to these questions:

1.  How many taxi fares in the dataset had a total amount greater than $100?


## Solution 1

```{r}
#| label: collect-1

```



# Using the dplyr API in arrow

## Problems

1.  Use the `dplyr::filter()` and `stringr::str_ends()` functions to return a subset of the data which is a) from September 2020, and b) the value in `vendor_name` ends with the letter "S".

2.  Try to use the `stringr` function `str_replace_na()` to replace any `NA` values in the `vendor_name` column with the string "No vendor" instead. What happens, and why?

3.  Bonus question: see if you can find a different way of completing the task in question 2.

## Solution 1

```{r}
#| label: collect-sol1

```

## Solution 2

```{r}
#| label: collect-sol2

```

## Solution 3

```{r}
#| label: collect-sol3

```


